An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-12-17 mixedwindow.tex
Minor changes to phrasing of empirical results

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process that is believed to
potentially contain information about $y_{t+1}$ and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value%
\footnote{It will be clear momentarily why the summation begins at
  $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\ep_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

We deviate slightly from the previous section's introduction by
allowing for multiple alternative models, as in \cite{HuW:10}. This
allowance is crucial if we want the statistic to be empirically
useful, since almost every empirical analysis considers several
alternative models at once.  Each of these alternative models is
denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estiatmed with a
rolling window of length $R$.

@@

Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97}.

@@

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

Finally, we define some notation for the \oos\ statistic. The
adjusted \oos\ loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

This assumption is much less restrictive than in \cite{Wes:96}.  As in
\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
rule out pathological cases---for example, letting both the benchmark
and the alternative models be perfectly correlated white noise. In
\citet{Wes:96}, this assumption is a restriction on the \dgp\ as well
as the forecasting models, but in this paper it is a restriction only
on the models.

@@

Asymptotic normality of the \oos\ average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
In Theorem~\ref{res:1}, define the variables
$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.

Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

Clearly, the main use of this theorem is to test the null hypothesis
$\E f_t = 0$.

The following remarks are relevant to Theorem~\ref{res:1}:

\begin{rem}
  Forecasters are usually interested in the one-sided alternative that
  $\E f_t > 0$; i.e. that the alternative model is expected
  to forecast better than the benchmark.
\end{rem}

@@

Define $\X' = [x_1,\dots,x_T]$

\begin{align*}
  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
\end{align*}

\newcommand{\K}[1]{K(\tfrac{#1}{w})}

Define the general covariance estimator:
\begin{align*}
  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
\end{align*}

Define the \mds\ covariance estimator:
\begin{align*}
  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
\end{align*}

>>>>

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value%
\footnote{It will be clear momentarily why the summation begins at
  $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\ep_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

We deviate slightly from the previous section's introduction by
allowing for multiple alternative models, as in \cite{Whi:00} and \cite{HuW:10}. This
modification is crucial if we want the statistic to be empirically
useful, since almost every empirical analysis considers several
alternative models at once.  Each of these alternative models is
denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estimated with a
rolling window of length $R$.

@@

Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.

@@

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts are otherwise unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

Finally, we define some notation for the \oos\ statistic. The
adjusted \oos\ loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.

Our last assumption is on the asymptotic variance of $\fb^*$.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb^*$ is positive definite.
\end{asmp}
This assumption is much less restrictive than in \cite{Wes:96}.  As in
\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
rule out pathological cases---for example, letting both the benchmark
and the alternative models be perfectly correlated white noise. In
\citet{Wes:96}, this assumption is a restriction on the \dgp\ as well
as the forecasting models, but in this paper it is a restriction only
on the models.

@@

Asymptotic normality of the \oos\ average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} closely.

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
(define $F$ and $B$)

Note that Theorem~\ref{res:1} does not require any of the models to be
correctly specified. Asymptotic normality follows from the weak
dependence of the underlying series and from the design of the test
statistic. Typically these statistics are used to test the null
hypothesis that the benchmark model is correctly specified, which
implies that $\fh_t - \E f_t^*$ is an \mds\ as discussed in
Section~\ref{sec:1a}. This is especially appealing in our framework,
since the benchmark can be theoretically motivated so the \mds\ null
can be a test of forecaster rationality.
But that null hypothesis only affects the
estimator of $\Sigma$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1}
continues to hold under alternatives that satisfy Assumptions
\ref{a1} -- \ref{a4}.

Moreover, Theorem~\ref{res:1} can be used with a \hac\ estimator of
$\Sigma$ when a researcher wants to test the weaker hypothesis that
$\E \fb^* = 0$ but the benchmark may be misspecified. This approach
could be interpreted as an encompassing test as in \citet{HLN:98}, and
would test whether the alternative models contain additional
information not present in the benchmark model. In either case (\mds\
or non-\mds), this test is designed to have power against the
``encompassing'' alternative. The specific research question should
then determine whether the test should also reject if there are other
violations of rationality.

\newcommand{\K}[1]{K((#1)/w)}
For the next results, define the variables $\gh_t = \Fh \Bh
x_t(y_{t+1} - x_t'\bh_t)$, $\gb = \oavg{t} \gh_t$, and
\begin{align*}
  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^{T-1} x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
  &\text{and}&
  \Bh &= \Big(\tfrac1P \sum_{s=R+1}^{T-1} x_s x_s' \Big)^{-1}
\end{align*}
Then define the \hac\ covariance estimator $\Sigmah_1$ and the \mds\
covariance estimator $\Sigmah_2$ as
\begin{align*}
  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}
  \intertext{and}
  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
\end{align*}
where $K$ is a kernel that satisfies standard assumptions.

\begin{asmp}\label{a5}
  Fill in assumptions on $\K$.
\end{asmp}

Put a last result here about one-sided testing.

@@
